---
title: "hw2"
output:
  html_document: default
  pdf_document: default
date: "2022-10-06"
---

Set up:
```{r setup, echo = FALSE}
library(tidymodels)
library(tidyverse)
abalone <- read_csv("abalone.csv")
abalone
```


Question 1:
```{r question1}
ages <- abalone %>% 
  mutate(age = rings + 1.5)
hist(ages$age, main = "Histogram of Abalone Ages", 
     xlab = "Age")
ages
```


In this histogram, we see that the distribution of age is mostly centered around 
8 to 14 years old. There are very few abalone ages that are older than 15 and there are extremely older than 25 years old. The most common ages are between 10 and 12 years old as an unimodal, right-skewed distribution. 

Question 2
```{r question2}
set.seed(1500)

abalone_split <- initial_split(ages, prop = 0.80, 
                               strata = age)

train = training(abalone_split)
test = testing(abalone_split)

```


Question 3
```{r question3}
abalone_recipe <- recipe(age ~ ., data = train) %>% 
  step_rm(rings) %>%
  step_dummy(all_nominal_predictors()) %>%
  step_interact(terms = ~ starts_with("type"):shucked_weight +
                  longest_shell:diameter +
                  shucked_weight:shell_weight) %>%
  step_scale(all_numeric_predictors()) %>%
  step_center(all_numeric_predictors())
abalone_recipe
```

I shouldn't include rings to predict age since rings are directly related to age as we would just add 1.5 years to rings and we would automatically know the age 
of the abalone.


Question 4
```{r question4}
lm_model <- linear_reg() %>% 
  set_engine("lm")
lm_model
```


Question 5
```{r question5}
lm_wflow <- workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(abalone_recipe)

lm_fit <- fit(lm_wflow, train)
lm_fit %>%
  extract_fit_parsnip() %>%
  tidy()

lm_fit
```


Question 6
```{r question6}
gather_data <- data.frame(type = "F", longest_shell = 0.50, diameter = 0.10, 
                          height = 0.30, whole_weight = 4, shucked_weight = 1, 
                          viscera_weight = 2, shell_weight = 1, rings = 0)

predict(lm_fit, new_data = gather_data)
```


Based on the information given, the abalone age is predicted to be around 24 years old. 


Question 7
```{r question7}
multi_metric <- metric_set(rsq, rmse, mae)

train_res <- predict(lm_fit, new_data = train %>% 
                       select(-age))

train_res <- bind_cols(train_res, train %>% 
                         select(age))

multi_metric(train_res, truth = age, 
                estimate = .pred)
```

Based on the results, we see that the R squared value is around 0.551. This 
means that there is a correlation (although not an extremely strong one, but still a strong one) between our predicted values and response values. 